Tugas UTS

### 2024-02-26 Project/Tugas UTS.Rmd
Update

#3. Menghitung Jacknife Estimator
teta_i <- ybar/ (xbar+ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta_i)
var_jk <- (n-1)/ n *sum( (teta_i - mean(teta_i))^2 )
se_jk <- sqrt(var_jk)
teta_jk; var_jk; se_jk
```

@@

# Kasus 3

```{r}

```

# Perbandingan Semua Cara

@@

teta_i <- ybar/ (xbar +ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta_i)

var_jk <- (n-1)/ n *(sum(teta_i^2) -(n *mean(teta_i)^2))
se_jk <- sqrt(var_jk)

@@

>>>>

#3. Menghitung Jacknife Estimator
teta_i <- ybar/ (xbar+ybar)
teta_jk <- n *teta_hat -(n-1) *mean(teta_i)
var_jk <- (n-1)/ n *sum( (teta_i - mean(teta_i))^2 )
se_jk <- sqrt(var_jk)
teta_jk; var_jk; se_jk
```

```{r}
par(mfrow=c(2,2))
hist(d1[,2]); hist(d1[,3])
hist(y); hist(x)
```

@@

# Kasus 1 cara 2

@@

teta. <- ybar/ (xbar +ybar)
teta_jk <-n *teta_hat -(n-1) *mean(teta.)

var_jk <- (n-1)/ n *(sum(teta.^2) -(n *mean(teta.)^2))
se_jk <- sqrt(var_jk)

@@

Bandingkan dengan cara 1:

```{r}
ragamTheta2; sqrt(ragamTheta2)
```

Sebaran

```{r}
par(mfrow=c(2,2))
hist(d1[,1]); hist(d1[,1])
hist(y); hist(x)
```
